Visualizing example of predicted TAD boundaries

### 2020-08-14 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
updated figures/tables

source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrandomForest.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

@@

```{r}
tadData <- createTADdata(bounds.GR=bounds.GR,
                         resolution=5000,
                         genomicElements.GR=genomicElements.GR,
                         featureType="distance",
                         resampling="rus",
                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))=="CHR22")],
                         predictCHR=NULL,
                         seed=123)
```

@@

```{r}
bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                     preprocess=FALSE, 
                                     CHR="CHR22", 
                                     resolution=5000)

pt <- preciseTAD(bounds.GR=bounds.GR,
                      genomicElements.GR=genomicElements.GR,
                      featureType="distance",
                      CHR="CHR22",
                      chromCoords=list(17000000,19000000),
                      tadModel=tadModel[[1]],
                      threshold=1.0,
                      flank=NULL,
                      verbose=TRUE,
                      seed=123,
                      parallel=FALSE,
                      cores=NULL,
                      splits=NULL,
                      method.Dist="euclidean",
                      DBSCAN=TRUE,
                      DBSCAN_params=list(5000,3), 
                      method.Clust=NULL,
                      PTBR=TRUE,
                      CLARA=FALSE,
                      samples=100)

saveRDS(pt, "C:/Users/stili/Downloads/pt_chr21_15150000_17270000")
```

@@

```{r}
tadModel <- readRDS("Z:/TAD_data_analysis/miscellaneous/tadModel.rds")
pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")

@@

#seqDataTest <- c(17389000:18011000)
#seqDataTest <- c(25745000:26176000)
#seqDataTest <- c(15150000:17270000)
seqDataTest <- c(70595000:71525000)

#CHR="CHR22"
#CHR="CHR21"
CHR="CHR1"

@@

predprobdata <- data.frame(#basenum=c(17389000:18011000),
                           #basenum=c(15150000:17270000),
                           basenum=c(70595000:71525000),
                           prob=predictions)
predprobdata$predicted <- ifelse(predprobdata$basenum %in% start(pt[[2]]), "Yes", "No")
predprobdata$called <- ifelse(predprobdata$basenum %in% start(pt[[3]]), "Yes", "No")

>>>>

source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrandomForest.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe2.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

@@

```{r}
tadData <- createTADdata(bounds.GR=bounds.GR,
                         resolution=5000,
                         genomicElements.GR=genomicElements.GR,
                         featureType="distance",
                         resampling="rus",
                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))=="CHR14")],
                         predictCHR="CHR14",
                         seed=123)
```

@@

```{r}
bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                     preprocess=FALSE, 
                                     CHR="CHR14", 
                                     resolution=5000)

pt <- preciseTAD(bounds.GR=bounds.GR,
                      genomicElements.GR=genomicElements.GR,
                      featureType="distance",
                      CHR="CHR14",
                      chromCoords=list(50085000,50800000),
                      tadModel=tadModel[[1]],
                      threshold=1,
                      flank=NULL,
                      verbose=TRUE,
                      seed=123,
                      parallel=FALSE,
                      cores=NULL,
                      splits=NULL,
                      method.Dist="euclidean",
                      DBSCAN=TRUE,
                      DBSCAN_params=list(5000,3),
                      method.Clust=NULL,
                      PTBR=TRUE,
                      CLARA=TRUE,
                      samples=100)

#saveRDS(pt, "C:/Users/stili/Downloads/pt_chr21_15150000_17270000")
```

@@

```{r}
#tadModel <- readRDS("Z:/TAD_data_analysis/miscellaneous/tadModel.rds")
#pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")

@@

#seqDataTest <- c(17389000:18011000)
#seqDataTest <- c(25745000:26176000)
#seqDataTest <- c(15150000:17270000)
seqDataTest <- c(50085000:50800000)

#CHR="CHR22"
#CHR="CHR21"
CHR="CHR14"

@@

predprobdata <- data.frame(#basenum=c(17389000:18011000),
                           #basenum=c(15150000:17270000),
                           basenum=c(50085000:50800000),
                           prob=predictions)
predprobdata$predicted <- ifelse(predprobdata$basenum %in% start(pt[[2]]), "Yes", "No")
predprobdata$called <- ifelse(predprobdata$basenum %in% start(pt[[3]]), "Yes", "No")
